On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-12 documents/paper.tex
Adaptive timestep apparently working

For instance, we wondered why we might not see such resonances in bodily tissues. Approximately similar nanoscopic structures exist in humans; for instance, nuclear pores (120 nm) and the famous microtubules (10x50 nm).

@@

[Liu 2009] cite [Edwards, Swicord 1984], saying: "It was proposed that a hydration layer surrounding DNA molecules could lower the viscoelastic transition
frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption". But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision and showing previous results to be an artifact of the measurement equipment.

@@

We demonstrate this form factor because, superficially, there are fewer people than there are places. Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.

@@

It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.

@@

@@

@@

We began experimentally by building a scaled version of [Mueller 2008]'s active antenna in microstrip, using a CEL mosfet.

@@

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

The authors of the original paper on

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work. Alex Dainis' videos on sterile technique were also useful.

@@

Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially.

>>>>

For instance, it is reasonable to wonder why we might not see such resonances in bodily tissues. Approximately similar nanoscopic structures exist in humans, such as nuclear pores (120 nm) and the famous microtubules (10x50 nm).

@@

[Liu 2009] cite [Edwards, Swicord 1984], saying: "It was proposed that a hydration layer surrounding DNA molecules could lower the viscoelastic transition
frequency, raise the quality factor of confined acoustic vibrations, and result in a microwave resonant absorption".

But [Adair 2002]'s [Foster 1987] seem to quite conclusively put the kibosh on that idea, demonstrating no resonances in DNA with 20x higher precision than previous work, showing previous results to be an artifact of the measurement equipment.

@@

Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.

We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.

@@

It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons. Airborne phased-arrays.

@@

It is commonly claimed that FR4 is a 'slow' substrate, and that the high loss tangent of ~0.02 makes it unsuitable for microwave systems.

However, with this PCB substrate, a loss of only 0.026 dB/mm on signals of minimum 0 dBm. We are also only minimally concerned with $S_{11}$ reflections, noise, or spurs (viruses do not have a discriminating palate), so precise impedance control is not required; the wideband VCO sweep accomodates for any variations in resonant frequency due to wide manufacturing tolerances.

@@

Initially,

Not having a good analytical understanding, we resorted to using a purely computational method.

@@

We began experimentally by building a scaled version of [Mueller 2008]'s active antenna on FR4, using a CEL mosfet.

@@

Figures are not forthcoming,

Given the supply difficulties of comparatively simple materials such as Tyvek at pandemic scales, it is difficult to imagine that RF semiconductor production can be immediately re-tasked and scaled to this degree.

\paragraph{\textbf{Vacuum RF triode}}\

One concern is the large filament heater power, which prevents the use of low-cost button cells for power. Use of cold-cathode field-emitter arrays would alleviate this issue, but at the cost of complexity.

Small tungsten incandescent lights are available down to 0.05 watts. With a suitable high-efficiency cathode coating, a pulsed heater power of less than 0.02

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Acknowledgements}\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This paper is not novel enough to deserve this chapter, but those to be acknowledged are.

The authors of the original papers deserve the credit for this entire work; it is rare that such a is served on a silver platter.

Professor Shahramian's excellent video blog {\it The Signal Path} inspired this work.

Dr. Dainis' videos on microbiological technique were also useful.

@@

Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially. Brian
